The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-06 analysis/paper/paper.qmd
Update object names

## Bigrams
emu_theses_bigrams <- emu_theses |> 
  get_ngrams(n = 2, title_col = "title", text_col = "text_clean", stem = TRUE)

spacyr::spacy_parse(emu_theses_bigrams$w_1)
data.frame(emu_theses_bigrams$w_1, textstem::lemmatize_words(emu_theses_bigrams$w_1))

@@

example_lemma <-list()
for (i in 1:10) {
  example_lemma[[i]] <- extract_rand_window(emu_theses_bigrams$w_1,10)
}

@@

bigram_counts <- emu_theses_bigrams |> 
  count(w_1, w_2, sort = TRUE)

bigram_stem_counts <- emu_theses_bigrams |> 
  count(w_1_stem, w_2_stem, sort = TRUE)

@@

## Bigram tf-idf
bigram_tf_idf <- emu_theses_bigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

@@

emu_theses_bigrams_top <- emu_theses_bigrams |>
  group_by(title) |>
  count(ngram, sort = TRUE) |>
  slice_max(n, n = 20) |>        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  ungroup() |>
  mutate(bigram = reorder(ngram, n))

emu_theses_bigrams_top_all <- emu_theses_bigrams |>
  count(ngram, sort = TRUE) |>
  slice_max(n, n = 20) |>        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  mutate(ngram = reorder(ngram, n))

emu_theses_bigrams_top |>
  filter(title == unique(title)[1:10]) |> 
  ggplot(aes(x = ngram, y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2) +
  theme(legend.position = "none") 
```

>>>>

## Bigrams
emu_bigrams <- emu_theses |> 
  get_ngrams(n = 2, title_col = "title", text_col = "text_clean", stem = TRUE)

spacyr::spacy_parse(emu_bigrams$w_1)
data.frame(emu_bigrams$w_1, textstem::lemmatize_words(emu_bigrams$w_1))

@@

example_lemma <-list()
for (i in 1:10) {
  example_lemma[[i]] <- extract_rand_window(emu_bigrams$w_1,10)
}

@@

bigram_counts <- emu_bigrams |> 
  count(w_1, w_2, sort = TRUE)

bigram_stem_counts <- emu_bigrams |> 
  count(w_1_stem, w_2_stem, sort = TRUE)

@@

## Bigram tf-idf
bigram_tf_idf <- emu_bigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

@@

emu_bigrams_top <- emu_bigrams |>
  group_by(title) |>
  count(ngram, sort = TRUE) |>
  slice_max(n, n = 20) |>        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  ungroup() |>
  mutate(bigram = reorder(ngram, n))

emu_bigrams_top_all <- emu_bigrams |>
  count(ngram, sort = TRUE) |>
  slice_max(n, n = 20) |>        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  mutate(ngram = reorder(ngram, n))

emu_bigrams_top |>
  filter(title == unique(title)[1:10]) |> 
  ggplot(aes(x = ngram, y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2) +
  theme(legend.position = "none") 
```
